Supporting Information

### 2018-03-06 SupportingInformation.Rmd
more editorial changes

#utility function for calculating all the stats we want
calcstats<-function(v,f,nm)
{
  #calculate the stats
  res<-c()
  #f(v[,1],v[,2],0,.5),
  #        f(v[,1],v[,2],0.5,1),
  #        f(v[,1],v[,2],0,.25),
  #        f(v[,1],v[,2],0.25,.5),
  #        f(v[,1],v[,2],.5,.75),
  #        f(v[,1],v[,2],.75,1))
  for (lbd in seq(from=0,to=0.9,by=0.1))
  {
    res<-c(res,f(v[,1],v[,2],lbd,lbd+.1))
  }

  #name the result vector
#  h<-paste(nm,c(0,0.5,0,0.25,0.5,0.75,seq(from=0,to=0.9,by=0.1)),"to",
#                    c(0.5,1,0.25,0.5,0.75,1,seq(from=0,to=0.9,by=0.1)+.1),sep='')
  h<-paste(nm,c(seq(from=0,to=0.9,by=0.1)),"to",
                    c(seq(from=0,to=0.9,by=0.1)+.1),sep='')
  h<-gsub(".","p",h,fixed=T)
  names(res)<-h

@@

<!--Now save the plot to the results folder-->
```{r plot_soilCN_graphic_approach, echo=F}
x<-seq(from=0.05,to=0.95,by=0.1)
xlimits<-c(0,1)

#plotting layout, units inches
xht<-0.5
ywd<-0.5
titleht<-.25
panht<-1.5
panwd<-3
gap<-.05
totwd<-ywd+2*panwd+2*gap
totht<-xht+3*panht+3*gap+titleht
pdf(file="./Results/stat_results/stat_soilCN//CNdata_NonparamTailDep.pdf",width=totwd,height=totht)

@@

<!--Now include the plot in the Rmd output-->
```{r show_plot_soildCN,echo=F}
fig_nums("soilCN_nonparam",display=F)
```
![Nonparametric tests for tail dependence and other deviations from a normal copula for soil C and N data. As described in Methods, each statistic was computed on the data using the ranges $0-0.1$, $0.1-0.2$, ..., $0.9-1$ (red lines), and was also computed using the same ranges for 1000 normal-copula surrogate datasets (dashed lines show 0.025 and 0.975 quantiles of these results and dotted lines show 0.005 and 0.995 quantiles).  When red lines were outside dashed lines, text at the top of plots indicates how many surrogate values the data value was less than or greater than.](./Results/stat_results/stat_soilCN//CNdata_NonparamTailDep.pdf)

>>>>

#utility function for calculating all the stats we want
calcstats<-function(v,f,nm)
{
  #calculate the stats
  res<-c()
  for (lbd in seq(from=0,to=0.9,by=0.1))
  {
    res<-c(res,f(v[,1],v[,2],lbd,lbd+.1))
  }

  #name the result vector
  h<-paste(nm,c(seq(from=0,to=0.9,by=0.1)),"to",
                    c(seq(from=0,to=0.9,by=0.1)+.1),sep='')
  h<-gsub(".","p",h,fixed=T)
  names(res)<-h

@@

<!--Now create the plot and save it to the results folder-->
```{r plot_soilCN_graphic_approach, echo=F}
x<-seq(from=0.05,to=0.95,by=0.1)
xlimits<-c(0,1)

#plotting layout, units inches
xht<-0.5
ywd<-0.5
titleht<-.25
panht<-1.5
panwd<-3
gap<-.05
totwd<-ywd+2*panwd+2*gap
totht<-xht+3*panht+3*gap+titleht
pdf(file="./Results/stat_results/stat_soilCN/CNdata_NonparamTailDep.pdf",width=totwd,height=totht)

@@

As described in Methods, each of our statistics, as computed for the 
ranges $0-0.1$, $0.1-0.2$, ..., $0.9-1$, was compared to the distributions 
of values of the same statistic (with the same ranges) on 1000 normal-copula 
surrogate datasets with similar Kendall or Spearman correlations, in different 
runs (`r figure_nums("soilCN_nonparam",display="c")`). Because the correlation 
used in the Cor statistic is the Spearman correlation, Spearman-preserving surrogates
should be used, so the top-left panel of `r figure_nums("soilCN_nonparam",display="c")`
should be ignored (DAN: need to fix this). Results indicate
DAN: continue here.

<!--Now give the plot a number so it can be refered to-->
```{r show_plot_soildCN,echo=F}
fig_nums("soilCN_nonparam",display=F)
```
![Nonparametric tests for tail dependence and other deviations from a normal copula for soil C and N data. As described in Methods, each statistic was computed on the data using the ranges $0-0.1$, $0.1-0.2$, ..., $0.9-1$ (red lines), and was also computed using the same ranges for 1000 normal-copula surrogate datasets (dashed lines show 0.025 and 0.975 quantiles of these results and dotted lines show 0.005 and 0.995 quantiles).  When red lines were outside dashed lines, text at the top of plots indicates how many surrogate values the data value was less than or greater than.](./Results/stat_results/stat_soilCN/CNdata_NonparamTailDep.pdf)
